A Cost-Aware Approach to Adversarial Robustness in Neural Networks

### 2024-08-22 main.tex

\documentclass[conference]{IEEEtran}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{algorithm}
\usepackage{algpseudocode}

\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\minimise}{\textrm{minimise}}
\DeclareMathOperator*{\maximise}{\textrm{maximise}}
\newcommand{\Ie}{\textit{I.e.}\xspace}
\newcommand{\ie}{\textit{i.e.}\xspace}
\newcommand{\Eg}{\textit{E.g.}\xspace}
\newcommand{\eg}{\textit{e.g.}\xspace}
\newcommand{\probP}{\text{I\kern-0.15em P}}
\newcommand{\tl}[1]{\textit{[{\color{red}#1}]}}
\newcommand{\cm}[1]{\textit{{\color{blue}#1}}}
\newcommand{\erik}[1]{\textit{[{\color{brown}Erik: #1}]}}
\newcommand{\mr}[1]{\textit{[{\color{brown}Mohammed: #1}]}}
\begin{document}
\title{A Cost-Aware Approach to Adversarial Robustness in Neural Networks}

\author{}
% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
% \author{\IEEEauthorblockN{1\textsuperscript{st} Charles Meyers}
% \IEEEauthorblockA{\textit{Dept. of Computing Science} \\
% \textit{Umeå University}\\
% Umeå, Sweden \\
% cmeyers@cs.umu.se}
% \and
% \IEEEauthorblockN{2\textsuperscript{nd} Mohammad Reza}
% \IEEEauthorblockA{\textit{Elastisys} \\
% % \textit{Umeå University}\\
% % Lund, Sweden \\
% mohammad.saleh@elastisys.com}
% \and
% \IEEEauthorblockN{3\textsuperscript{rd} Tommy Löfstedt}
% \IEEEauthorblockA{\textit{Dept. of Computing Science} \\
% \textit{Umeå University}\\
% Umeå, Sweden \\
% tommy@cs.umu.se}
% \and
% \IEEEauthorblockN{4\textsuperscript{th} Erik Elmroth}
% \IEEEauthorblockA{\textit{Dept. of Computing Science} \\
% \textit{Umeå University}\\
% Umeå, Sweden \\
% elmroth@cs.umu.se}
% }

@@

@@

Recently, machine learning (ML) using deep neural networks has become a popular way to classify large amounts of data --- with applications ranging from medical imaging~\cite{ai_medical_imaging} to aviation~\cite{ai_aviation} and from security~\cite{ai_security,ai_luggage,ai_prison} to self-driving cars~\cite{ai_automotive}. 
Statistical learning theory~\cite{vcdimension} provides us no guarantees about the generalization performance of deep neural networks due to the massive number of tunable parameters. To overcome this, neural networks need large amounts of data~\cite{desislavov2021compute,bailly2022effects} to train ever-larger model~\cite{desislavov2021compute}, which has yielded increasingly marginal gains on test-set accuracy~\cite{sun2017revisiting}. It is also clear that reaching safety-critical standards using test-set accuracy would require an infeasibly large test set~\cite{meyers}. Therefore, we propose using accelerated failure time models to simulate edge-cases and verify models using a small number of samples.

@@

ML pipelines play a crucial role in the development and deployment of robust and accurate models. However, managing complex pipelines across diverse CPU and GPU architectures, ensuring robustness against adversarial attacks, and understanding the relationship between computational cost, model loss, and prediction accuracy remain ongoing challenges.
One popular solution is using a network of interconnected services~\cite{panchal2024reusable,hasselbring2017microservice,zhou2022online,singh2023load} where a \textit{service} is the smallest component of a ``cloud-native" software stack. In the context of ML, that might be some software component meant for training, inference, pre-processing, sampling, or any other arbitrarily small part of the data pipeline. 
A service \textit{mesh} typically consists of a set of interconnected components or proxies deployed alongside the services within the system.  These components facilitate various capabilities and functionalities essential for managing the communication between services. Kubernetes has become one of the largest open source projects on the code-sharing website Github~\cite{k8s-size} and provides a framework for managing, monitoring, and networking a self-scaling set of tools across arbitrary software and hardware architectures using a service mesh. For ML applications, these services are often divided into ``training" and ``inference" configurations that often have distinct hardware and software configurations~\cite{wang2019benchmarking}. In this work, we leveraged Kubernetes~\cite{k8s} to manage a multi-stage ML pipeline (see Figure~\ref{fig:experiments}) and measure the power and cost of training and evaluating the pipeline (see Figure~\ref{fig:architecture}) across a variety of different hardware architectures (see Table~\ref{tab:hardware}).

@@

\begin{figure}
    \centering
    \includegraphics[width=.45\textwidth]{plots/experiment.pdf}
    \caption{For each dataset and hardware combination, a random state parameter was chosen at random to decide the test and train sets. Next, model parameters and attack parameters are chosen at random. After 128 random trials, the TPE algorithm attempts to maximize benign and adversarial accuracy while minimizing training time.}
    \label{fig:experiments}
\end{figure}

@@

Accuracy measures the vulnerability or susceptibility of the model to failures. A larger accurate indicates a higher rate of true classifications, signifying a weaker model in terms of \textit{robustness} against (noise-induced) failures. Throughout, we use the terminology \textit{benign} accuracy to refer to the performance on the test set using unperturbed data and \textit{adversarial} to refer to the performance in the presence of additive noise that is intended to confuse the model. The subscripts \textit{ben} and \textit{adv} are used respectively. The accuracy, $\lambda$, is defined as
\begin{equation}
    \lambda:= \mathrm{Accuracy} := 1 - \frac{\mathrm{False~Classifications}}{\mathrm{Total~Classifciations}},
    \label{eq:acc}
\end{equation}
which is generally assumed to indicate the rate of successes in real-world data sampled from the same distribution as the training data~\cite{tan2021critical}. However, the normal test/train split methodology consistently overestimates the model's performance in the presence of adversarial noise~\cite{croce_reliable_2020.
In addition, it ignores the run-time cost of a given architectural decision, caring only about accuracy on benchmark data~\cite{desislavov2021compute,bailly2022effects}. Additionally, it has been shown that it is trivial to generate adversarial counter examples that reveal the test/train split methodology to be optimistic at best~\cite{carlini_towards_2017,adversarialpatch,pixelattack,hopskipjump,biggio_poisoning_2013,chakraborty_adversarial_2018,dohmatob_generalized_2019,meyers}.

@@

@@

\subsubsection{Choosing the best AFT Model}

To choose a best-fit from the possible AFT functions, one should prepare the collected metrics and scores and then compare them using \textit{e.g.}, Akaike Information Criterion (AIC), Bayesian Information Criteria (BIC), or Concordance, as per the best-practices for this methodology~\cite{aft_models,kleinbaum1996survival}. For AIC and BIC, that means choosing the smallest value. Concordance, however, is a number between $0$ and $1$ that quantifies the degree to which the survival time is explained by the model, where a $1$ reflects a perfect explanation~\cite{kleinbaum1996survival} and 0.5 reflects random chance. By evaluating $\mathbb{E}_{S_\theta}[T]$ under extreme perturbations, one can test the model and minimize the number of evaluated samples~\cite{aft_models,kleinbaum1996survival} rather than relying on the $> 10^{12}$ samples as required by IEC61508~\cite{IEC61508}. We also noted the integrated calibration index (ICI) as well as the error at the median (E50)~\cite{ici}. These are the mean absolute difference between observed and predicted probabilities and the median absolute difference between observed and predicted probabilities, respectively~\cite{ici}. Then, the fitted AFT models were plotted using that compares the fitted AFT model to a cubic spline fit to the data~\textit{et al.}~\cite{ici}  to visually inspect each model for goodness-of-fit (see Figure~\ref{fig:qq}). \cm{Additionally, the data were split into a training set that was used to fit the model (80\%) and an unseen test set (20\%) and the concordance, ICI, and E50 were measured for both.}

\subsection{Survival Time}
\label{accelerated}

Using accelerated failure time models under adverse ones (accelerated failure time), $S_{adv}$. The survival time for is
$$
    S_{\theta} := S(t_i; x, y, \varepsilon \mid \theta) \mathrm{~~where~~} 0 < \varepsilon \leq \varepsilon_{max}.
$$
\cm{where $\varepsilon$ -- or noise distance -- is treated as a covariate}.
This can also be thought of in terms of the accelerated failure time assumption~\cite{kleinbaum1996survival}
\begin{equation} \label{assumption}
    S_\theta(t) = S_0 \left( \frac{t}{\phi_\theta(x)} \right)
\end{equation}
where $\phi$ is some acceleration factor described by the joint effect of the covariates and $S_0$ is the baseline hazard function (where the effect of the covariates are 0). This assumption means we can evaluate the generalization performance using a small number of adversarial samples~\cite{kleinbaum1996survival}, with our precision coming from careful time measurements rather than massive test sets.
However, in order to find the optimal hyper-parameter configurations for both the model and attack, one must search this space systematically.

ML models are typically trained by examining the effect of the entire hyper-parameter space on the resulting accuracy. However, the number of hyper-parameter combinations are often infinite or at least exponential in the number of hyper-parameters,
making it infeasible to exhaustively evaluate the entire hyper-parameter search space. Additionally, the goals of test-set accuracy and adversarial accuracy are often at odds~\cite{carlini_towards_2017} --- with several researchers noting an inverse relationship between model accuracy and model robustness~\cite{carlini_towards_2017,meyers,dohmatob_generalized_2019}. Therefore, a proper search would keep this dual-objective in mind.
To optimise for adversarial and benign accuracy simultaneously, we propose the use of the Tree-structure Parzen Estimator (TPE) because it has been shown to converge  over tens or hundreds of trials rather the the 1000s of trials required by other multi-objective optimisation algorithms like CMAES or NGSA-II~\cite{ozaki2020multiobjective,optuna,tpe_params}.

@@

@@

To assess the energy consumption of the experiments deployed on a Google Kubernetes Engine, the Kubernetes Efficient Power Level Exporter (KEPLER) was employed as measurement tool~\cite{amaral2023kepler}. This approach enables gathering energy consumption data on granular levels as it runs in Kubernetes cluster and capable of collecting energy consumption of Kubernetes components. In essence, KEPLER uses extended Berkeley Packet Filter (eBPF) to probe energy-related system stats and exports them as Prometheus metrics. The eBPF can be described as a lightweight and sandboxed virtual machine (VM) in kernel space. The eBPF programs are invoked by the kernel when certain events occur. Examples of such events include system calls or network activity. These processes enable deep analysis and full control over different events with low overhead~\cite{sedghpour@ebpf}. A diagram of the cloud architecture can be found in Figure~\ref{fig:architecture}. Finally, for a cost-effective model evaluation technique, all of the experiments were restricted to a single one-thousand United States dollar budget (a research grant from Google). Approximately 10\% of this was used for development and 90\% was used for the evaluations.

\begin{figure*}
    \centering
    \includegraphics[width=.8\textwidth]{plots/architecture.pdf}
    \caption{For our experiments we used four node pools from Google Cloud Platform, each has a particular responsibility. The first node pool includes 3 different nodes responsible for hosting monitoring services such as Prometheus and Grafana.  The other node pools each had one node with a specific GPU.  The KEPLER exporter is then deployed on each node as DaemonSet to monitor the resource usage.  All the storage requirements during the experimentation such as storage for experiments and monitoring data were then stored on storage provided by persistent volume claim (PVC). A PVC is a request for storage by user in Kubernetes which is then connected to the object storage.}
    \label{fig:architecture}
\end{figure*}

@@

For each hardware configuration and dataset, the TPE algorithm was used to select the hyper-parameters~\cite{ozaki2020multiobjective,zitzler2008quality}, and it was iterated for 1000 trials. This was chosen to be substantially larger than the 200 used successfully by Watanabe~\textit{et al.}~\cite{tpe_params} while still allowing for reasonable run times. In reality, the correct number of iterations will be determined by the frequency of local minima across the search space and the number of optimisation criteria where marginally more minima or criteria require significantly more trials to yield accurate results~\cite{legriel2010approximating}. Examining the effect of this and other TPE parameters on the total run-time and performance of this methodology was outside the scope of this work.
We used three optimisation criteria: benign accuracy, training time, and adversarial accuracy, seeking to maximize both benign and adversarial accuracy while minimizing training time (and therefore deployment cost). We selected a set of parameters as per the TPE algorithm and trained on 80\% of the samples for each of the MNIST, CIFAR10, and CIFAR100 datasets. Of the remaining samples, 100 were withheld to be attacked and used to evaluate the adversarial accuracy. Figure~\ref{fig:experiments} illustrates this methodology. For each dataset, we tested this on ten random splits of the data to create 10 unique test/train pairs. For each trial, we recorded attack generation time, model training time, model inference time, benign accuracy and adversarial accuracy, and the size of the training set, test set, and attack set. Using these values, we fit an AFT model to the number of failures (indicated by accuracy and sample size) and the attack generation time after adding dummy variables for the dataset and hardware device. Additionally, we approximate the AFT model using the methodology described in Algorithm~\ref{fig:alg}.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth,clip]{plots/combined/acc.pdf}
    \caption{Ben. and Adv. Accuracy Across Datasets and Hardware.}
    \label{fig:acc}
\end{figure}

\begin{figure*}[h]
    \centering
    \begin{subfigure}[b]{.8\textwidth}
        \includegraphics[width=\linewidth,clip]{plots/combined/time.pdf}
        \caption{Training (left), Prediction (center), and Attack (right) Times.}
        \label{fig:time}
    \end{subfigure}
    \begin{subfigure}[b]{.8\textwidth}
        \includegraphics[width=\linewidth,clip]{plots/combined/power.pdf}
        \caption{Training (left), Prediction (center), and Attack (right) Power Consumption.}
        \label{fig:power}
    \end{subfigure}
    \begin{subfigure}[b]{.8\textwidth}
        \includegraphics[width=\linewidth,clip]{plots/combined/cost.pdf}
        \caption{Training (left), Prediction (center), and Attack (right) Monetary Cost.}
        \label{fig:cost}
    \end{subfigure}
    \caption{This depicts the training, inference, and attack cost metrics for all hardware and datasets. For these plots, the y-axes have been scaled by the the number of samples for the sake of comparison.}
\end{figure*}

@@

\input{plots/combined/aft_comparison}  % Table II

@@

Table~\ref{tab:combined} shows the performance metrics for all three AFT models, as outlined in Section~\ref{survival_time}. A total 75\% of the available data were used to build the AFT models and 25\% were withheld for evaluation. The concordance is both strong ($>0.5$) and similar for all three AFT models and both the train and test sets. We observed no more than 1\% mean absolute error in the probabilities (ICI) and no error in the median probability (E50) across all three AFT models. Figure~\ref{fig:qq} depicts the observed and predicted probabilities for all three AFT models. For further analysis, we chose the Weibull AFT due to its superior fit in Figure~\ref{fig:qq}, and average test error of 1\% (ICI) and 0 error for the median sample (E50). We also see that these metrics are  functionally identical across all AFT models as well as between the test and train set of each model.

@@

% no keywords
% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\clearpage
\bibliographystyle{IEEEtran}
\bibliography{bibliography}

>>>>

\documentclass[conference]{IEEEtran}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage[type=\acronymtype]{glossaries}

\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\minimise}{\textrm{minimise}}
\DeclareMathOperator*{\maximise}{\textrm{maximise}}
\newcommand{\Ie}{\textit{I.e.}\xspace}
\newcommand{\ie}{\textit{i.e.}\xspace}
\newcommand{\Eg}{\textit{E.g.}\xspace}
\newcommand{\eg}{\textit{e.g.}\xspace}
\newcommand{\probP}{\text{I\kern-0.15em P}}
\newcommand{\tl}[1]{\textit{[{\color{red}#1}]}}
\newcommand{\cm}[1]{\textit{{\color{blue}#1}}}
\newcommand{\erik}[1]{\textit{[{\color{brown}Erik: #1}]}}
\newcommand{\mr}[1]{\textit{[{\color{brown}Mohammed: #1}]}}

\input{glossary}
\makeglossaries
\begin{document}

\title{A Cost-Aware Approach to Adversarial Robustness in Neural Networks}

@@

\author{}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
% \author{\IEEEauthorblockN{1\textsuperscript{st} Charles Meyers}
% \IEEEauthorblockA{\textit{Dept. of Computing Science} \\
% \textit{Umeå University}\\
% Umeå, Sweden \\
% cmeyers@cs.umu.se}
% \and
% \IEEEauthorblockN{2\textsuperscript{nd} Mohammad Reza}
% \IEEEauthorblockA{\textit{Elastisys} \\
% % \textit{Umeå University}\\
% % Lund, Sweden \\
% mohammad.saleh@elastisys.com}
% \and
% \IEEEauthorblockN{3\textsuperscript{rd} Tommy Löfstedt}
% \IEEEauthorblockA{\textit{Dept. of Computing Science} \\
% \textit{Umeå University}\\
% Umeå, Sweden \\
% tommy@cs.umu.se}
% \and
% \IEEEauthorblockN{4\textsuperscript{th} Erik Elmroth}
% \IEEEauthorblockA{\textit{Dept. of Computing Science} \\
% \textit{Umeå University}\\
% Umeå, Sweden \\
% elmroth@cs.umu.se}
% }

@@

Recently, \acrfull{ml} using deep neural networks has become a popular way to classify large amounts of data --- with applications ranging from medical imaging~\cite{ai_medical_imaging} to aviation~\cite{ai_aviation} and from security~\cite{ai_security,ai_luggage,ai_prison} to self-driving cars~\cite{ai_automotive}.
Statistical learning theory~\cite{vcdimension} provides us no guarantees about the generalization performance of deep neural networks due to the massive number of tunable parameters. 
To overcome this, neural networks need large amounts of data~\cite{desislavov2021compute,bailly2022effects} to train ever-larger model~\cite{desislavov2021compute}, which has yielded increasingly marginal gains on test-set accuracy~\cite{sun2017revisiting}.
It is also clear that reaching safety-critical standards using test-set accuracy would require an infeasibly large test set~\cite{meyers}. 
Therefore, we propose using \acrfull{aft} models to simulate edge-cases and verify models using a small number of samples.

@@

ML pipelines play a crucial role in the development and deployment of robust and accurate models. However, managing complex pipelines across diverse \acrfull{cpu} and \acrfull{gpu}  architectures, ensuring robustness against adversarial attacks, and understanding the relationship between computational cost, model loss, and prediction accuracy remain ongoing challenges.
One popular solution is using a network of interconnected services~\cite{panchal2024reusable,hasselbring2017microservice,zhou2022online,singh2023load} where a \textit{service} is the smallest component of a ``cloud-native" software stack. In the context of ML, that might be some software component meant for training, inference, pre-processing, sampling, or any other arbitrarily small part of the data pipeline. 
A service \textit{mesh} typically consists of a set of interconnected components or proxies deployed alongside the services within the system.  These components facilitate various capabilities and functionalities essential for managing the communication between services. Kubernetes has become one of the largest open source projects on the code-sharing website Github~\cite{k8s-size} and provides a framework for managing, monitoring, and networking a self-scaling set of tools across arbitrary software and hardware architectures using a service mesh. For ML applications, these services are often divided into ``training" and ``inference" configurations that often have distinct hardware and software configurations~\cite{wang2019benchmarking}. In this work, we leveraged Kubernetes~\cite{k8s} to manage a multi-stage ML pipeline (see Figure~\ref{fig:experiments}) and measure the power and cost of training and evaluating the pipeline (see Figure~\ref{fig:architecture}) across a variety of different hardware architectures (see Table~\ref{tab:hardware}).

@@

@@

Accuracy measures the vulnerability or susceptibility of the model to failures. A larger accurate indicates a higher rate of true classifications, signifying a weaker model in terms of \textit{robustness} against (noise-induced) failures. Throughout, we use the terminology \textit{benign} accuracy to refer to the performance on the test set using unperturbed data and \textit{adversarial} to refer to the performance in the presence of additive noise that is intended to confuse the model. The subscripts \textit{ben} and \textit{adv} are used respectively. The accuracy, $\lambda$, is defined as
\begin{equation}
    \lambda:= \mathrm{Accuracy} := 1 - \frac{\mathrm{False~Classifications}}{\mathrm{Total~Classifciations}},
    \label{eq:acc}
\end{equation}
which is generally assumed to indicate the rate of successes in real-world data sampled from the same distribution as the training data~\cite{tan2021critical}. However, the normal test/train split methodology consistently overestimates the model's performance in the presence of adversarial noise~\cite{croce_reliable_2020}.
In addition, it ignores the run-time cost of a given architectural decision, caring only about accuracy on benchmark data~\cite{desislavov2021compute,bailly2022effects}. Additionally, it has been shown that it is trivial to generate adversarial counter examples that reveal the test/train split methodology to be optimistic at best~\cite{carlini_towards_2017,adversarialpatch,pixelattack,hopskipjump,biggio_poisoning_2013,chakraborty_adversarial_2018,dohmatob_generalized_2019,meyers}.

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{plots/experiment.pdf}
    \caption{For each dataset and hardware combination, a random state parameter was chosen at random to decide the test and train sets. Next, model parameters and attack parameters are chosen at random. After 128 random trials, the TPE algorithm attempts to maximize benign and adversarial accuracy while minimizing training time by tuning the model parameters. The random seed for the data split and the attack parameters are sampled independently from this optimization, which is why they are colored differently. The model tuning (blue-box) is discussed in Section~\ref{optimisation}. After the trials are completed, several AFT models are fit (see: Section~\ref{survival_time}) and compared (see: Section~\ref{best-fit}) using the process depicted in the purple box. Finally we conduct the cost analysis outlined in Section~\ref{cost} (green box).}
    \label{fig:experiments}
\end{figure*}

ML models are typically trained by examining the effect of the entire hyper-parameter space on the resulting accuracy. However, the number of hyper-parameter combinations are often infinite or at least exponential in the number of hyper-parameters,
making it infeasible to exhaustively evaluate the entire hyper-parameter search space. Additionally, the goals of test-set accuracy and adversarial accuracy are often at odds~\cite{carlini_towards_2017} --- with several researchers noting an inverse relationship between model accuracy and model robustness~\cite{carlini_towards_2017,meyers,dohmatob_generalized_2019}. Therefore, a proper search would keep this dual-objective in mind.
To optimise for adversarial and benign accuracy simultaneously, we propose the use of the Tree-structure Parzen Estimator (TPE) because it has been shown to converge  over tens or hundreds of trials rather the the 1000s of trials required by other multi-objective optimisation algorithms like CMAES or NGSA-II~\cite{ozaki2020multiobjective,optuna,tpe_params}. In addition, we seek to minimize the training time in order to maximize the number of hyper-parameters that can be examined on a fixed budget. Further discussion of the cost analysis can be found in Section~\ref{cost}.

@@

\subsubsection{Survival Time}
\label{accelerated}
~\cm{
By using adversarial samples (see: Equation~\ref{eq:adv_success}, failures can be induced. The likelihood of that failure is dependent on the amount of adversarial noise, $\varepsilon$~\cite{meyers_aft}. That is, we can say the probability of success at time, $t$ is inversely proportional to  noise distance, $\varepsilon$, and  directly proportional to some baseline survival function, $S_0$, such that the parameterised survival time $S_{\theta}(t)$ is:
$$
S_{\theta}(t) \propto  S_0 \left( \frac{t}{\varepsilon} \right)
$$
This can also be thought of in terms of the accelerated failure time assumption~\cite{kleinbaum1996survival}
\begin{equation} \label{assumption}
    S_\theta(t) = S_0 \left( \frac{t}{\phi_\theta(x)} \right),
\end{equation}
where $\phi$ is some acceleration factor described by the joint effect of the covariates:
$$
phi_{\theta}(x) = \exp( \beta_0 \varepsilon + \beta_1 x_1 + \cdots + \beta_n x_n),
$$ 
and where $\varpsilon, x$ are covariates and $\beta_0 \cdots \beta_n$ describe the fitted parameters.
}
This assumption means we can evaluate the generalization performance using a small number of adversarial samples with our precision coming from careful time measurements rather than massive test sets~\cite{kleinbaum1996survival,meyers_aft}.
However, in order to find the optimal hyper-parameter configurations for both the model and attack, one must search this space systematically.

\subsection{Choosing the best AFT Model}
\label{best-fit}
To choose a best-fit from the possible AFT functions, one should prepare the collected metrics and scores and then compare them using \textit{e.g.}, Akaike Information Criterion (\acrshort{aic}), Bayesian Information Criteria (\acrshort{bic}), or Concordance, as per the best-practices for this methodology~\cite{aft_models,kleinbaum1996survival}. 
For \acrshort{aic} and \acrshort{bic}, that means choosing the smallest value. Concordance, however, is a number between $0$ and $1$ that quantifies the degree to which the survival time is explained by the model, where a $1$ reflects a perfect explanation~\cite{kleinbaum1996survival} and 0.5 reflects random chance. By evaluating $\mathbb{E}_{S_\theta}[T]$ under extreme perturbations, one can test the model and minimize the number of evaluated samples~\cite{aft_models,kleinbaum1996survival} rather than relying on the $> 10^{12}$ samples as required by IEC61508~\cite{IEC61508}. 
We also noted the integrated calibration index (\acrshort{ici}) as well as the error at the 50th percentile \acrshort{e50}~\cite{ici}. 
These are the mean absolute difference between observed and predicted probabilities and the median absolute difference between observed and predicted probabilities, respectively~\cite{ici}. 
Then, the fitted AFT models were plotted using that compares the fitted AFT model to a cubic spline fit to the data~\textit{et al.}~\cite{ici}  to visually inspect each model for goodness-of-fit (see Figure~\ref{fig:qq}). \cm{Additionally, the data were split into a training set that was used to fit the model (80\%) and an unseen test set (20\%) and the concordance, ICI, and E50 were measured for both.}

@@

In security analysis, it is  routine to think in optimistic terms for both the attacker and defender. In cryptography, these ideal attack- and defence-scenarios are used to test the computational feasibility of subverting a particular cryptographic system~\cite{kamal2017study,leurent2020sha} (\textit{e.g.}, whether or not a given cryptographic method should be considered ``broken"). 
Using AFT, one can model the Pareto front --- the set of points that are superior to all others in the search space --- of either party~\cite{zitzler2008quality}. By using a whitebox attack to generate the failures, we ensure that our defender operates under the worst case scenario while the attacker operates under their best case scenario to yield a worst-case failure rate.
As such, we center our analysis on the whitebox Fast Gradient Method~\cite{fgm} (see Eq.~\ref{eq:fgm}) which is both effective and fast~\cite{meyers}. If the cost to a model builder is much larger than the cost to an attacker ($C_t \gg C_a$), then it is  clear that the model is ``broken" in this cryptographic sense and can be discarded as ineffective.

@@

To assess the energy consumption of the experiments, \Gls{kepler} deployed on a was used to measure the power consumption of each experiment~\cite{amaral2023kepler}. This approach enables gathering energy consumption data on granular levels as it runs in Kubernetes cluster and capable of collecting energy consumption of Kubernetes components. In essence, KEPLER uses extended Berkeley Packet Filter to probe energy-related system stats and exports them as Prometheus metrics. This filter can be described as a lightweight and sandboxed virtual machine (VM) in kernel space. The filter programs are invoked by the kernel when certain events occur. Examples of such events include system calls or network activity. These processes enable deep analysis and full control over different events with low overhead~\cite{sedghpour@ebpf}. A diagram of the cloud architecture can be found in Figure~\ref{fig:architecture}. Finally, for a cost-effective model evaluation technique, all of the experiments were restricted to a single one-thousand United States dollar budget (a research grant from Google). Approximately 10\% of this was used for development and 90\% was used for the evaluations.
\cm{Over the course of the evaluations, 6\% of the budget went to the storage, 6\% to the monitoring, and the remaining 88\% went the GPUs. TODO: Calculate total cost/gpu for 1000 trials.}.

\begin{figure*}
    \centering
    \includegraphics[width=.9\textwidth]{plots/architecture.pdf}
    \caption{For our experiments we used four node pools from Google Cloud Platform, each has a particular responsibility. The first node pool includes 3 different nodes responsible for hosting monitoring services such as Prometheus and Grafana.  The other node pools each had one node with a specific GPU.  The KEPLER exporter is then deployed on each node as DaemonSet to monitor the resource usage.  All the storage requirements during the experimentation such as storage for experiments and monitoring data were then stored on storage provided by persistent volume claim (PVC). A PVC is a request for storage by user in Kubernetes which is then connected to the object storage.}
    \label{fig:architecture}
\end{figure*}

@@

For each hardware configuration and dataset, the TPE algorithm was used to select the hyper-parameters~\cite{ozaki2020multiobjective,zitzler2008quality}, and it was iterated for 1000 trials. This was chosen to be substantially larger than the 200 used successfully by Watanabe \textit{et al.}~\cite{tpe_params} while still allowing for reasonable run times~\cite{legriel2010approximating}. 
% In reality, the correct number of iterations will be determined by the frequency of local minima across the search space and the number of optimisation criteria where marginally more minima or criteria require significantly more trials to yield accurate results~\cite{legriel2010approximating}. Examining the effect of this and other TPE parameters on the total run-time and performance of this methodology was outside the scope of this work.
We used three optimisation criteria: benign accuracy, training time, and adversarial accuracy, seeking to maximize both benign and adversarial accuracy while minimizing training time (and therefore deployment cost). We selected a set of parameters as per the TPE algorithm and trained on 80\% of the samples for each of the MNIST, CIFAR10, and CIFAR100 datasets. Of the remaining samples, 100 were withheld to be attacked and used to evaluate the adversarial accuracy. Figure~\ref{fig:experiments} illustrates this methodology. For each dataset, we tested this on ten random splits of the data to create 10 unique test/train pairs. For each trial, we recorded attack generation time, model training time, model inference time, benign accuracy and adversarial accuracy, and the size of the training set, test set, and attack set. Using these values, we fit an AFT model to the number of failures (indicated by accuracy and sample size) and the attack generation time after adding dummy variables for the dataset and hardware device. Additionally, we approximate the \acrshort{aft} model using the methodology depicted in Figure~\ref{fig:experiments}.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth,clip]{plots/combined/acc.pdf}
    \caption{\cm{Benign and adversarial accuracy across all hardware and datasets for all 1000 trials using plots that depict the distribution of the y-axis values using the width of the plot. Each color is a different device and the datasets are displayed along the x-axis. Outliers are denoted with a white dot.}}
    \label{fig:acc}
\end{figure}

\begin{figure*}[h]
    \centering
    \begin{subfigure}[b]{.8\textwidth}
        \includegraphics[width=\linewidth,clip]{plots/combined/time.pdf}
        \caption{}
        \label{fig:time}
    \end{subfigure}
    \begin{subfigure}[b]{.8\textwidth}
        \includegraphics[width=\linewidth,clip]{plots/combined/power.pdf}
        \caption{}
        \label{fig:power}
    \end{subfigure}
    \begin{subfigure}[b]{.8\textwidth}
        \includegraphics[width=\linewidth,clip]{plots/combined/cost.pdf}
        \caption{}
        \label{fig:cost}
    \end{subfigure}
    \caption{This depicts the training, inference, and attack cost metrics for all hardware and datasets \cm{ for all 1000 trials using plots that depict the distribution of the second axis values using the width of the plot. Each color is a different device and the datasets are displayed along the first axis. Outliers are denoted with a white dot.}
    For these plots, the second axes have been scaled by the number of samples for the sake of comparison.}
\end{figure*}

@@

\begin{table*}
\centering
\caption{Comparison of AFT Models on the combined dataset. \cm{\acrshort{aic} and \acrshort{bic} are measures of goodness-of-fit, with a smaller one being preferred. Concordance is a value between 0 and 1 that reflects how what proportion of events (failures) can be explained by the model. \acrshort{ici} measures the average error between a cubic-spline and the model and \acrshort{e50} measures the median error between the spline and the model. These measured on both the train and test sets of the collected data, with the latter being denoted ``Test''.}}
\label{tab:combined}
\begin{tabular}{lrrrrrrrr}
\toprule
 & AIC & BIC & Concordance & Test Concordance & ICI & Test ICI & E50 & Test E50 \\
\midrule
Weibull & -2.11e+04 & -2.11e+04 & 0.84 & 0.83 & 0 & 0.01 & 0 & 0 \\
Log Logistic & -2.18e+04 & -2.18e+04 & 0.84 & 0.83 & 0.01 & 0.01 & 0 & 0 \\
Log Normal & -2.25e+04 & -2.25e+04 & 0.84 & 0.83 & 0.01 & 0 & 0 & 0 \\
\bottomrule
\end{tabular}
\end{table*}

@@

Table~\ref{tab:combined} shows the performance metrics for all three AFT models, as outlined in Section~\ref{survival_time}. A total 75\% of the available data were used to build the AFT models and 25\% were withheld for evaluation. The concordance is both strong ($>0.5$) and similar for all three AFT models and both the train and test sets. We observed no more than 1\% mean absolute error in the probabilities \acrshort{ici} and no error in the median probability \acrshort{e50} across all three AFT models. Figure~\ref{fig:qq} depicts the observed and predicted probabilities for all three AFT models. For further analysis, we chose the Weibull AFT due to its superior fit in Figure~\ref{fig:qq}, and average test error of 1\% \acrshort{ici} and 0 error for the median sample \acrshort{e50}. We also see that these metrics are  functionally identical across all AFT models as well as between the test and train set of each model.

@@

% no keywords
% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle
\clearpage
\printglossary[type=\acronymtype]
\clearpage
\bibliographystyle{IEEEtran}
\bibliography{bibliography}
